Mining Patents Data through Semantic Network Analysis\bigskip\\ \textit{Project Proposal}

### 2015-10-19 Docs/Proposal/patents.tex
Update patents.tex

>>>>

Every patent is associated with many details that have been made available by national and international patent offices. First, each patent is associated with one or several technological fields which are chosen from a list by patent office specialists after careful review of the content of the patent (see IPC class). Second, every patent has to make a list of citations to all the patents used in the process, this naturally define a network between entities that have some technologies in common. From these two features innovation economists have created various indices to measure the quality of a patent ( number of citations, scope of technological field...).

Two other indicators are of particular interest for us: originality and radicalness. The originality measure is
defined by Hall \textit{et al.} (2001) \cite{Hall2001} as $Ori_{i}%
=1-\displaystyle\sum_{j=1}^{n_{i}}{cit_{i,j}^{2}}$ where $cit_{i,j}$ is the
percentage of citations made by patent $i$ to a patent in class $j$ out of
$n_{i}$ technological classes to which patent $i$ belongs. If the scope of
technologies which the patent uses and cites is large, then the originality
measure will be high. Radicalness is more difficult to define. It is
constructed in the same way as the originality index but here we only consider
the technology classes of patents cited by patent $i$ but to which patent $i$
does not belong.
